visualFields 1.x

### 2025-05-09 vignette.Rmd
Commented code in Vignette because of incompatibility with glr function.

The *glr* function performs linear regression on global parameters. In the following example, the patient loses `r round(abs(glr(getgl(example3), type = "md")$sl), 2)` dB each year and this change is statistically significant, with a $p$-value < `r format(ceiling(1000 * glr(getgl(example3), type = "md")$pval) / 1000, nsmall = 3)`.

@@

md_regression <- data.frame(time = glr(getgl(example3), type = "md")$years,
           md = glr(getgl(example3), type = "md")$data)

globallm <- glr(getgl(example3), type = "md")
slope <- globallm$sl
intercept <- globallm$int
pval <- globallm$pval

ggplot(md_regression, aes(x = time, y =md)) +
  geom_point() +
  geom_abline(slope = slope, intercept = intercept)

print(paste("intercept:", intercept))
print(paste("slope:", slope))
print(paste("p-value:", pval))

>>>>

The *glr* function performs linear regression on global parameters. In the following example, the patient loses `r # round(abs(glr(getgl(example3))$sl), 2)` dB each year and this change is statistically significant, with a $p$-value < `r # format(ceiling(1000 * glr(getgl(example3))$pval) / 1000, nsmall = 3)`.

@@

# md_regression <- data.frame(time = glr(getgl(example3))$years,
#            md = glr(getgl(example3))$data)
# 
# globallm <- glr(getgl(example3))
# slope <- globallm$sl
# intercept <- globallm$int
# pval <- globallm$pval
# 
# ggplot(md_regression, aes(x = time, y = md)) +
#   geom_point() +
#   geom_abline(slope = slope, intercept = intercept)
# 
# print(paste("intercept:", intercept))
# print(paste("slope:", slope))
# print(paste("p-value:", pval))
